[Result, but poetic]: Does LLM Use Improve Data Science Education?

### 2024-07-12 paper/paper.qmd
Tweak the model bit
more setup, added literature

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

@@

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

@@

first_model <-
  readRDS(file = here::here("outputs/models/first_model.rds"))
```

>>>>

---
title: "[Result, but poetic]: Does LLM Use Improve Data Science Education?"
subtitle: "Evidence from a Canadian Undergraduate Statistics Course"
author: 
  - Rohan Alexander
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/llms-achievement."
date: today
date-format: long
abstract: "Blah Blah Blah Blah"
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
```

@@

@@

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```
